Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-05-15 paper/main.tex
Updates from Overleaf

\section{Simulations}
\subsection{Risk versus discovery: an illustrative example}
It is natural to ask under what circumstances we may recover a classifier that performs very well

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4in]{../results/figures/ChangingDelta.png}
    \caption{\textbf{A}: Component-aligned, axis-aligned; \textbf{B}: Not component-aligned, axis-aligned; \textbf{C}: Component-aligned, not axis-aligned; \textbf{D}: Not component-aligned, not axis-aligned.\label{fig:examplefigures}}
\end{figure}

>>>>

\section{Simulations}
\subsection{Risk versus discovery: an illustrative example}
It is natural to ask under what circumstances we may recover a classifier that performs very well, but fails to discover the true subspace. To elucidate one example where the relationship between the performance of the base/ensembled classifiers and the discovery rate (power) is subtle, we return to the linear discriminant analysis setting. We restrict to two dimensions, so that $X$ has one 'signal' covariate and one 'noise' covariate. We may then directly control the signal-to-noise ratio via the variable $\Delta$. In Figure~\ref{fig:ChangingDelta} we investigate, by simulation, the effect of varying $\Delta$ on the expected power of a single choice of projection ($B_1 = 1$), when we use projections with $d=1$ and an LDA base classifier on a training set of 200 samples, with selection determined by empirical risk on the training set.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4in]{../results/figures/ChangingDelta.png}
    \caption{The relationship between signal-to-noise ratio and discovery rate.\label{fig:ChangingDelta}}
\end{figure}
